Finding Quality Issues in SKOS Vocabularies

### 2012-03-24 analysis.tex
added additional results
added analysis data
fixed first table

We used Sindice and available listings\footnote{\url{http://www.w3.org/2001/sw/wiki/SKOS/Datasets}} to learn about existing SKOS vocabularies. Table~\ref{vocabs} lists our representative vocabulary selection and shows that the vocabularies differ in size and application domain: the \emph{Gemeenschappelijke Thesaurus Audiovisuele Archieven (GTAA)} is vocabulary from the media domain, \emph{Eurovoc} and the \emph{Integrated Public Sector Vocabularies (PSV)} cover public sector concepts, the \emph{Medical Subject Headings (MeSH)} and \emph{Peroxisome Knowledge Base (PXV)} are from the (bio-)medical domain, the \emph{Geonames Ontology} covers locations, the \emph{Thesaurus for Economics (STW)} and \emph{North American Industry Classification System (NAICS)} are vocabularies from the economics and business area and the \emph{DBPedia Categories} reflect Wikipedia's user-generated categorization system. We also include the \emph{Meketre} vocabulary, which defines Egyptology-related concepts, and the non-public \emph{Thesaurus Landesverteidigungsakademie (LVAk)}, which we generated from CSV files provided by the vocabulary maintainers. A zip-file containing all 14 public vocabulariesx we used in our analysis, can be downloaded from: \url{http://www.github.com/cmader/???}.

\begin{table}[h]
\label{tab:vocs}
\caption{Analyzed SKOS vocabularies}
\centering
\begin{tabular}{p{6cm}cccccccc}
\textbf{Vocabulary} & \rotatebox{90}{\textbf{Version/last mod.}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Auth. Concepts}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} & \rotatebox{90}{\textbf{Collections}}\\
\toprule
Gemeenschappelijke Thesaurus Audiovisuele Archieven (GTAA) & 2010/08/25 & 171991 && 178776 & 50892 & 343980 & 9 & 0 \\
\hline
Geonames Ontology & 2.2.1 & 671 && 671 & 0 & 671 & 9 & 0 \\
\hline
Medical Subject Headings (MeSH) & ? & 24626 && 150617 & 38858 & 0 & 0 & 0 \\
\hline
Peroxisome Knowledge Base (PXV) & 1.6 & 2112 && 3628 & 2695 & 1716 & 1 & 0 \\
\hline
Eurovoc & 5.0 & 6797 && 457788 & 18491 & 15512 & 128 & 0 \\
\hline
Integrated Public Sector Vocabulary (IPSV) & 2.00 & 4732 && 7945 & 13843 & 4483 & 3 & 0 \\
\hline
AGROVOC & 1.3 & 32035 && 620629 & 65934 & 32085 & 1 & 0 \\
\hline
DBpedia Categories & ? & 743410 && 740352 & 1490316 & 0 & 0 & 0 \\
\hline
University of Southampton Pressinfo & 2011/02/24 & 1125 && 0 & 0 & 0 & 0 & 0 \\
\hline
New York Times People (NYTP) & 2010/06/22 & 4979 && 4979 & 0 & 4979 & 1 & 0 \\
\hline
Library of Congress Subject Headings (LCSH) & ? & 459182 && 746076 & 595754 & 815816 & 19 & 0 \\
\hline
Meketre & 2011/07/07 & 422 && 569 & 1698 & 6 & 2 & 0 \\
\hline
Thesaurus for Economics (STW) & 8.06 & 6524 && 31189 & 57907 & 6531 & 1 & 0 \\
\hline
North American Industry Classification System (NAICS) & 2012 & 4175 && 0 & 8684 & 2235 & 1 & 0 \\
\hline
Thesaurus Landesverteidigungsakademie (LVAk) & n/a & 13411 && 17250 & 16346 & 0 & 0 & 0 \\
\bottomrule
\end{tabular}
\label{vocabs}
\end{table}

@@

\begin{table}[h]
\label{tab:results}
\caption{Results of the quality checking functions}
\begin{tabular}{p{4cm}ccccccccccccccc}
\textbf{Metric} & \rotatebox{90}{\textbf{GTAA}} & \rotatebox{90}{\textbf{Geonames}} & \rotatebox{90}{\textbf{MeSH}} & \rotatebox{90}{\textbf{PXV}} & \rotatebox{90}{\textbf{Eurovoc}} & \rotatebox{90}{\textbf{IPSV}} & \rotatebox{90}{\textbf{Agrovoc}} & \rotatebox{90}{\textbf{DBpedia}} & \rotatebox{90}{\textbf{Pressinfo}} & \rotatebox{90}{\textbf{NYTP}} & \rotatebox{90}{\textbf{LCSH}} & \rotatebox{90}{\textbf{Meketre}} & \rotatebox{90}{\textbf{STW}} & \rotatebox{90}{\textbf{NAICS}} & \rotatebox{90}{\textbf{LVAk}} \\
\toprule
Omitted or Invalid Language Tags & 0 & 0 && 1578 & n/a & 0 & 0 & 0 & 1224 & 0 & 18 & 0 & 2 & n/a & 13411 \\

Incomplete Language Coverage & 0 & 0 && 0 & n/a & 0 & 32035 & 0 & 0 & 0 & 0 & 420 & 6456 & n/a & 0 \\

Undocumented Concepts & 96850 & 0 && 1918 & 5341 & 4551 & 32035 & tba & 1125 & 4094 & tba & 422 & 5236 & 3259 & 13411 \\

@@

Weakly Connected Components & 621 & 0 & & 10 & 4 & 1 & 4 & 1506 & 0 & 0 & 22131 & 5 & 1 & 1 & 11 \\

Cyclic Hierarchical Relations &&&&&&&&&&&&&&& \\

Valueless Associative Relations &&&&&&&&&&&&&&& \\

Solely Transitively Related Concepts &&&&&&&&&&&&&&& \\

Omitted Top Concepts &&&&&&&&&&&&&&& \\

Top Concept Having Broader Concepts &&&&&&&&&&&&&&& \\

@@

Undefined SKOS Resources &&&&&&&&&&&&&&& \\

>>>>

We used Sindice and available listings\footnote{\url{http://www.w3.org/2001/sw/wiki/SKOS/Datasets}} to learn about existing SKOS vocabularies. Table~\ref{tab:vocabs} lists our representative vocabulary selection \todo{CM}{alphabetically} and shows that the vocabularies differ in size and application domain: the \emph{Gemeenschappelijke Thesaurus Audiovisuele Archieven (GTAA)} is vocabulary from the media domain, \emph{Eurovoc} and the \emph{Integrated Public Sector Vocabularies (PSV)} cover public sector concepts, the \emph{Medical Subject Headings (MeSH)} and \emph{Peroxisome Knowledge Base (PXV)} are from the (bio-)medical domain, the \emph{Geonames Ontology} covers locations, the \emph{Thesaurus for Economics (STW)} and \emph{North American Industry Classification System (NAICS)} are vocabularies from the economics and business area and the \emph{DBPedia Categories} reflect Wikipedia's user-generated categorization system. We also include the \emph{Meketre} vocabulary, which defines Egyptology-related concepts, and the non-public \emph{Thesaurus Landesverteidigungsakademie (LVAk)}, which we generated from CSV files provided by the vocabulary maintainers. A zip-file containing all 14 public vocabulariesx we used in our analysis, can be downloaded from: \url{http://www.github.com/cmader/???}.

\begin{table}
\label{tab:vocabs}
\caption{Analyzed SKOS vocabularies}

\begin{center}

\resizebox{\textwidth}{!} {

\setlength{\extrarowheight}{5pt}

\begin{tabular}{p{6cm}ccccccccc}

\textbf{Vocabulary} & \rotatebox{90}{\textbf{Abbrev.}} & \rotatebox{90}{\textbf{Version/last mod.}} & \rotatebox{90}{\textbf{Concepts}} & \rotatebox{90}{\textbf{Auth. Concepts}} & \rotatebox{90}{\textbf{Labels}} & \rotatebox{90}{\textbf{Semantic Rel.}} & \rotatebox{90}{\textbf{Aggregation Rel.}} & \rotatebox{90}{\textbf{Concept Schemes}} & \rotatebox{90}{\textbf{Collections}}\\
\toprule
Gemeenschappelijke Thesaurus Audiovisuele Archieven & \textbf{GTAA} & 2010/08/25 & 171991 && 178776 & 50892 & 343980 & 9 & 0 \\
\hline
Geonames Ontology & \textbf{Geonames} & 2.2.1 & 671 & 671 & 671 & 0 & 671 & 9 & 0 \\
\hline
Medical Subject Headings & \textbf{MeSH} & ? & 24626 & 24626 & 150617 & 38858 & 0 & 0 & 0 \\
\hline
Peroxisome Knowledge Base & \textbf{PXV} & 1.6 & 2112 & 1686 & 3628 & 2695 & 1716 & 1 & 0 \\
\hline
The EU's multilingual thesaurus & \textbf{Eurovoc} & 5.0 & 6797 && 457788 & 18491 & 15512 & 128 & 0 \\
\hline
Integrated Public Sector Vocabulary & \textbf{IPSV} & 2.00 & 4732 && 7945 & 13843 & 4483 & 3 & 0 \\
\hline
Agricultural Thesaurus & \textbf{AGROVOC} & 1.3 & 32035 && 620629 & 65934 & 32085 & 1 & 0 \\
\hline
DBpedia Categories & \textbf{DBPedia} & ? & 743410 && 740352 & 1490316 & 0 & 0 & 0 \\
\hline
University of Southampton Pressinfo & \textbf{Pressinfo} & 2011/02/24 & 1125 && 0 & 0 & 0 & 0 & 0 \\
\hline
New York Times People & \textbf{NYTP} & 2010/06/22 & 4979 && 4979 & 0 & 4979 & 1 & 0 \\
\hline
Library of Congress Subject Headings & \textbf{LCSH} & ? & 459182 && 746076 & 595754 & 815816 & 19 & 0 \\
\hline
Middle Kingdom tombs of Ancient Egypt Thesaurus & \texttt{Meketre} & 2011/07/07 & 422 && 569 & 1698 & 6 & 2 & 0 \\
\hline
Thesaurus for Economics & \textbf{STW} & 8.06 & 6524 && 31189 & 57907 & 6531 & 1 & 0 \\
\hline
North American Industry Classification System & \textbf{NAICS} & 2012 & 4175 && 0 & 8684 & 2235 & 1 & 0 \\
\hline
Thesaurus Landesverteidigungsakademie & \textbf{LVAk} & n/a & 13411 && 17250 & 16346 & 0 & 0 & 0 \\
\bottomrule
\end{tabular}

}
\end{center}
\end{table}

@@

\begin{table}[h]
\label{tab:results}
\caption{Results of the quality checking functions}
\begin{tabular}{p{4cm}ccccccccccccccc}
\textbf{Metric} & \rotatebox{90}{\textbf{GTAA}} & \rotatebox{90}{\textbf{Geonames}} & \rotatebox{90}{\textbf{MeSH}} & \rotatebox{90}{\textbf{PXV}} & \rotatebox{90}{\textbf{Eurovoc}} & \rotatebox{90}{\textbf{IPSV}} & \rotatebox{90}{\textbf{Agrovoc}} & \rotatebox{90}{\textbf{DBpedia}} & \rotatebox{90}{\textbf{Pressinfo}} & \rotatebox{90}{\textbf{NYTP}} & \rotatebox{90}{\textbf{LCSH}} & \rotatebox{90}{\textbf{Meketre}} & \rotatebox{90}{\textbf{STW}} & \rotatebox{90}{\textbf{NAICS}} & \rotatebox{90}{\textbf{LVAk}} \\
\toprule
Omitted or Invalid Language Tags & 0 & 0 & 23950 & 1578 & n/a & 0 & 0 & 0 & 1224 & 0 & 18 & 0 & 2 & n/a & 13411 \\

Incomplete Language Coverage & 0 & 0 & 0 & 0 & n/a & 0 & 32035 & 0 & 0 & 0 & 0 & 420 & 6456 & n/a & 0 \\

Undocumented Concepts & 96850 & 0 & 1807 & 1918 & 5341 & 4551 & 32035 & tba & 1125 & 4094 & tba & 422 & 5236 & 3259 & 13411 \\

@@

Weakly Connected Components & 621 & 0 & 4 & 10 & 4 & 1 & 4 & 1506 & 0 & 0 & 22131 & 5 & 1 & 1 & 11 \\

Cyclic Hierarchical Relations & 0 & 0 & 4 & 0 & 0 & 0 & 0 & 1132 & 0 & 0 && 0 & 0 & 0 & 5 \\

Valueless Associative Relations & 9438 & 0 & 495 &&&&&&&&&&&& \\

Solely Transitively Related Concepts & 0 & 0 & 0 &&&&&&&&&&&& \\

Omitted Top Concepts & 9 & 9 & 0 &&&&&&&&&&&& \\

Top Concept Having Broader Concepts & 0 & 0 & 0 &&&&&&&&&&&& \\

@@

Undefined SKOS Resources & 0 & 0 & 1 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0  \\
